### 2016-08-10 R/ITHIM.Rmd
Conducted all pairwise comparisons of metro regions

```{r showMatrices}
meanWalkList$HHS1
meanWalkList$HHS2
meanCycleList$HHS1
meanCycleList$HHS2
```

@@

@@

<!--
#### DETAILS ON WONDER QUERY

@@

-->

```{r newMETs, echo = TRUE, eval = FALSE}
newMETsFile <- "~/GHI/data/ATUS/ATUS_to_METS_key.csv"
newMETs <- read.csv(file = newMETsFile, stringsAsFactors = FALSE, colClasses = c("character","character","character","character","numeric","character","character","character"))
dataColumns <- c(1,5)
D <- newMETs[,dataColumns]
metaData <- newMETs[,-dataColumns]
newMETs <- list(Data = D, metaData = metaData)
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))

```{r readnewMETs, echo = TRUE, eval = FALSE}
cpsFile <- "~/GHI/data/ATUS/atuscps_0311.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

```{r metKey, echo = TRUE, eval = FALSE}
allActivities <- colnames(summaryList$Data)
nonTravelActivities <- rownames(newMETs$metaData)[which(newMETs$metaData$Travel.related..Y.N. == "N")]
nonTravelActivities <- nonTravelActivities[which(nonTravelActivities %in% allActivities)]

```{r parameters}
(parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             ))

## Bay Area

@@

## National

>>>>

@@

```{r newMETs, echo = TRUE, eval = TRUE}
newMETsFile <- "~/GHI/data/ATUS/ATUS_to_METS_key.csv"
newMETs <- read.csv(file = newMETsFile, stringsAsFactors = FALSE, colClasses = c("character","character","character","character","numeric","character","character","character"))
dataColumns <- c(1,5)
D <- newMETs[,dataColumns]
metaData <- newMETs[,-dataColumns]
newMETs <- list(Data = D, metaData = metaData)
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))

```{r readnewMETs, echo = TRUE, eval = TRUE}
cpsFile <- "~/GHI/data/ATUS/atuscps_0311.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

```{r metKey, echo = TRUE, eval = TRUE}
allActivities <- colnames(summaryList$Data)
nonTravelActivities <- rownames(newMETs$metaData)[which(newMETs$metaData$Travel.related..Y.N. == "N")]
nonTravelActivities <- nonTravelActivities[which(nonTravelActivities %in% allActivities)]

```{r parameters, eval = TRUE}
(parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             ))

@@

```{r CRA}

CRA.fn <- function(i, j){
  foo <- compareModels( ITHIMList[[i]], ITHIMList[[j]])
  sum(unlist(foo$AF))
}

CRAMatrix <- matrix(NA, nrow = 10, ncol = 10)

for( i in 1:10 ){
  CRA <- c()
  for( j in 1:10 ){
    CRA <- c( CRA, CRA.fn(i, j))
  }
  CRAMatrix[i,] <- CRA
}

which(CRAMatrix == max(CRAMatrix), arr.ind = TRUE)

## DETAILS ON WONDER QUERY

@@

## Example (Bay Area)

@@

## Example (National)
